Legion: Expressing Locality and Independence with Logical Regions

### 2012-08-09 doc/sc2012/related.tex
Messing with DPJ paragraph in related work

Deterministic Parallel Java (DPJ) is a parallel extension of Java
that, like Legion, uses regions to express locality and does
dependence analysis at the granularity of conflicts on region
arguments to functions \cite{Bocchino09}.  As the name suggests, one
of the primary goals of DPJ is to provide a programming model that
guarantees determinism while also supporting parallelism.
As a result the programming model is more restrictive than Legion, as
there is no notion of weaker coherence properties of regions than
exclusive access (which is essential to determinism).  DPJ can express
the populate-then-partition style of using regions, but not the
partition-then-populate; overall, the language is more static, and
thus provides more guarantees and less flexibility than Legion.  
DPJ efforts have so far focused on JVM implementations on shared memory machines.

>>>>

Deterministic Parallel Java (DPJ) is a parallel extension of Java
that, like Legion, uses regions to express locality, but does
static dependence analysis on region
arguments to functions to find dependences\cite{Bocchino09}.  The primary goal of DPJ 
is to provide a programming model that
guarantees determinism while also supporting parallelism.
As a result, the DPJ programming model is more restrictive than Legion.  
DPJ only supports a static form of Legion's exclusive and atomic 
coherence modes which mandates the same coherence for the lifetime
of a region.  DPJ can express
the populate-then-partition style of using regions, but not the
partition-then-populate.  Overall, DPJ is more static, and
thus provides more guarantees and less flexibility than Legion.  
DPJ efforts have so far focused on JVM implementations on shared memory machines.
